### 2022-01-26 input/background.tex

Numerous studies addressed content indexing in geo-distributed
infrastructures ranging from centralized services to fully
decentralized approaches~\cite{squirrel}. We advocate for the latter
where \processes host the service themselves so they do not need to
request remote -- possibly far away third-party -- entities to
retrieve their content location.  In this paper, we tackle the content
indexing issue as a dynamic logical partitioning problem. This section
motivates our positioning and explains the shortcomings of existing
implementations.

@@

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other \processes of its new
content. \Process~$R$ can use uniform reliable
broadcast~\cite{hadzilacos1994modular} and epidemic
propagation~\cite{epidemic-protocol} to guarantee that
\begin{inparaenum}[(i)]
\item every \process eventually knows the content location
\item by efficiently using neighbor-to-neighbor communication.
\end{inparaenum}

\item [Location:]

>>>>

Numerous studies addressed content indexing in geo-distributed
infrastructures ranging from centralized services to fully
decentralized approaches~\cite{squirrel}. We advocate for the latter
where \processes host the service themselves so they do not need to
request remote -- possibly far away third-party -- entities to
retrieve content locations.  More precisely, we propose to consider the content
indexing issue as a dynamic logical partitioning problem. This section
motivates our positioning and explains the shortcomings of existing
implementations.

@@

Figure~\ref{fig:partition_intuition} depicts an infrastructure
comprising 17 interconnected \processes spread across France. In
Figure~\ref{fig:partition_intuitionA}, a single \Process~$R$ hosts the
content, so every other \process downloads from this \process when it
needs it. In that regard, \Process~$R$ only needs to disseminate a
message notifying all other \processes of its new
content. \Process~$R$ can use uniform reliable
broadcast~\cite{hadzilacos1994modular} and epidemic
propagation~\cite{epidemic-protocol} to guarantee that
\begin{inparaenum}[(i)]
\item every \process eventually knows the content location
\item by efficiently using neighbor-to-neighbor communication.
\end{inparaenum}
\textcolor{red}{Je ne vois pas l'interet des enums ici? ca casse la lecture}
\item [Location:]

### 2022-01-26 input/introduction.tex

Instead, a \process creating a replica should notify all and only
\processes that have no closer replica in the system. This would
create interconnected sets of \processes, or \emph{partitions},
gathered around a \emph{source} being their respective replica. A
\process deleting its replica should notify all members of its
partition so they can identify and rally their new closest
partition. Periodic advertisement protocols already provide both
operations~\cite{hemmati2015namebased, sohier2012physarum}. However,
their functioning requires
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item the use of synchronous communications~\cite{sohier2012physarum}
  or physical-time-based intervals tuned according to network topology
  parameters such as network diameter~\cite{hemmati2015namebased}.
\end{inparaenum}

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes can join, leave, or crash at any time. \NAME's
  efficiency relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.

>>>>

To mitigate the broadcasting overhead, a \process creating a replica
should notify all and only \processes that have no closer replica in
the system. This would create interconnected sets of \processes, or
\emph{partitions}, gathered around a \emph{source} being their
respective replica. A \process deleting its replica should notify all
members of its partition so they can identify and rally their new
closest partition. \TODO{Periodic advertisement protocols} already
provide both
operations~\cite{hemmati2015namebased,sohier2012physarum}. However,
their functioning requires
% TODO: A periodic protocol... why a periodic protocol solves the ''correct cast/scope''? I miss the point here 
\begin{inparaenum}[(i)]
\item to generate traffic even when the system is quiescent, and
\item the use of synchronous communications~\cite{sohier2012physarum}
  or physical-time-based intervals tuned according to network topology
  parameters such as network diameter~\cite{hemmati2015namebased}.
\end{inparaenum}

@@

\item [$\bullet$] We provide an implementation entitled \NAME that
  uses aforementioned principles to \underline{a}dapt its partitioning
  to creations and deletions of partitions even in dynamic systems
  where \nodes can join, leave, or crash at any time. \NAME's
  efficiency relies on a communication primitive called
  \underline{s}coped-broad\underline{cast} that enables epidemic
  dissemination of messages as long as receiving \processes verify an
  application-dependant predicate.
  \textcolor{red}{AS-Cast stands for Autonomous System-Cast since xAS means cross AS? what did I miss?}
